---
title       : Slidify Presentation of my shiny app.
subtitle    : Why should you use my app
author      : Laura Sanders
job         : R student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose of the app

The environment is imortant for all of the people.
And therefore also airquality.
The mean Ozone can be influenced by Solar Radiation.
The app shows the mean Ozone if a certain level of Solar Radiation is present in the air.

--- .class #id 

## How is the connection between Ozone and Solar.R determined



1. Exclude all missing variables
2. Create a model with Ozone as the depenedent variabele and Solar.R as the independent variable
3. Solar.R has a positive influence on the mean Ozone. The higher the amount of Solar.R the higher the mean Ozone
4. Create a shiny app in which people fill in the Solar.R value they have
5. If you push the submit button the new mean Ozone will be calculated for values between 7 and 334

---

## How does the formula look like


The Solar.R value has a positive influence on the mean Ozone.The function used to calculate the Ozone is as follows. 
```{r,echo=TRUE}
Solar.R<-10
Ozonedetermined<-18.5987278+0.1271653*Solar.R
```
Also, you can see the summary of the values where the model is based on.
```{r,echo=FALSE}
library(datasets)
data<-airquality
datamodel<-na.omit(data)
```
```{r,echo=TRUE}
summary(datamodel$Solar.R)
```


---

## Why use the app?

- positive influence on peoples health
- Less ill people 
- Less cost for the government
- People are less dependent on the government to warn them
- almost no costs involved for everyone with access to a computer



